Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-02-20 vertical-thermal-review.Rmd
acknowledgments word count

Text | word count | other | n
---|---|-----|--------------------
Total word count (excluding summary, references and legends) | 	9560 |	No. of figures | 	6 (all colour)
Summary|  	200 | 	No. of Tables | 	2  
Introduction|	391 |	No of Supporting Information files | 	6
Review of vertical gradients |	6484	||	 
Implications |	2408	 ||
Conclusions |	276	||
Acknowledgments | ##	||

>>>>

Text | word count | other | n
---|---|-----|--------------------
Total word count (excluding summary, references and legends) | 	9560 |	No. of figures | 	6 (all colour)
Summary|  	200 | 	No. of Tables | 	2  
Introduction|	391 |	No of Supporting Information files | 	6
Review of vertical gradients |	6484	||	 
Implications |	2408	 ||
Conclusions |	276	||
Acknowledgments | 43	||
